Benchmarking KiCS2

### 2014-10-08 benchmarks/benchmark_papers/kics2/bench_kics2.tex
PDF terminal for benchmark plots added

\begin{center}
\runcurry{benchNRevAndPlot 5.2 [500,1000..] "plot_all"}
\end{center}

@@

The following benchmark programs contain non-deterministic operations
or free variables. We evaluate the computation of all
solutions/values via DFS in various Curry systems:

@@

\subsection{Non-deterministic Benchmarks}

@@

>>>>

\begin{center}
\runcurry{benchNRevAndPlot 5.2 [500,1000..] "plot_all.pdf"}
\end{center}

@@

The following benchmark programs contain non-deterministic operations
or free variables. We evaluate the computation of all
solutions/values via the depth-first strategy (DFS)
with various Curry systems:

@@

\subsection{Search Strategy Benchmarks for KiCS2}

@@

These benchmarks are executed with the option ``\texttt{:set +parallel}''
and different run-time settings to influence the number
of threads used for the execution.
